\documentclass[11pt,openany]{book}
\ifdefined\amazontrimsize
  \usepackage[paperwidth=6in,paperheight=9in,margin=0.72in]{geometry}
\else
  \usepackage[a4paper,margin=2.6cm]{geometry}
\fi
\usepackage{fontspec}
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{tabularx}
\usepackage{enumitem}
\usepackage{makeidx}
\usepackage{setspace}
\usepackage[nopatch=footnote]{microtype}
\usepackage{fvextra}
\usepackage{xcolor}
\usepackage{float}
\DefineVerbatimEnvironment{CodeBlock}{Verbatim}{breaklines=true,breakanywhere=true,fontsize=\small}
\makeindex
\setstretch{1.14}
\setcounter{tocdepth}{1}
\setlength{\emergencystretch}{3em}
\sloppy
\pagestyle{plain}
\hypersetup{
  pdftitle={IT Professional Practice},
  pdfauthor={Greg Baker},
  hidelinks
}
\title{IT Professional Practice\\\large A Practical Course Reader}
\author{Greg Baker}
\date{Draft edition}
\newif\ifcoverpage
\coverpagetrue
\ifdefined\omitcoverpage
  \coverpagefalse
\fi

\begin{document}
\ifcoverpage
\begin{titlepage}
\thispagestyle{empty}
\vspace*{0.12\textheight}
{\Huge\bfseries IT Professional Practice\par}
\vspace{1.2em}
{\Large A Practical Course Reader\par}
\vfill
{\large Greg Baker\par}
{\large Draft edition\par}
\end{titlepage}
\fi

\frontmatter
\chapter*{About This Course Reader}
\addcontentsline{toc}{chapter}{About This Course Reader}
\setcounter{secnumdepth}{-1}
This is a professional-practice handbook for technical graduates who must operate, improve, buy, sell, and steward digital services responsibly. It is written for university students about to enter IT, data, software, support, platform, customer-success, sales-engineering, vendor-management, and digital-governance roles, and for early-career practitioners who have already discovered that real services are held together by more than code.


\index{change record}
\index{CRM}
\index{DevOps}
\index{ITIL}
\index{service desk}
The book is not trying to be an ITIL exam manual, a DevOps transformation book, a CRM sales text, or a startup operations guide. Those shelves already have strong books. This reader sits between them. Its job is to teach the conversations that early-career technical people keep being pulled into: the service desk ticket that becomes a change record, the sales promise that becomes an operational obligation, the incident review that becomes a product decision, the vendor contract that becomes next year's budget, and the dataset that cannot be treated as raw material just because it is easy to copy.



\subsection{The Course Map}


Read the course as one service story:



\begin{figure}[H]
\centering
\footnotesize
\renewcommand{\arraystretch}{1.18}
\begin{tabularx}{\linewidth}{@{}p{0.30\linewidth}X@{}}
\toprule
\textbf{Course movement} & \textbf{Professional question} \\
\midrule
Promise & What are we promising users, and what does good service look like? \\
Operating model & Who receives work, escalates it, changes it, measures it, and improves it? \\
Delivery pipeline & How do we change the service repeatedly without turning every release into a crisis? \\
Incident learning & What did the incident teach us about the system, and who owns the fix? \\
Vendor lifecycle & What commercial promise has operations inherited, and what evidence keeps the relationship honest? \\
Small org constraints & Which controls matter first when money, time, and specialist staff are scarce? \\
Data authority & Who has authority to share, reuse, maintain, and benefit from the artefact or dataset? \\
Capstone defence & Can the whole service design survive questions from operations, commercial, technical, and community perspectives? \\
\bottomrule
\end{tabularx}
\caption{The course arc: from service promise to defended service design.}
\end{figure}


\index{GitHub Actions}
\index{licence}
\index{open source}
\index{Salesforce}
\index{ServiceNow}
That map is the reason ServiceNow, GitHub Actions, Salesforce, vendor scorecards, open-source licences, and Indigenous data-governance frameworks belong in the same course. They are all places where technical work becomes accountable to other people.



\subsection{How To Use The Book And Site}


\index{capstone}
\index{DORA metrics}
\index{KPI}
\index{post-mortem}
\index{service level agreement}
The book carries the stable material: concepts, cases, vocabulary, decision patterns, and the professional judgement behind them. The companion site is the operational half of the course. It should carry the artefacts that change more often: ticket examples, post-mortem templates, SLA and KPI worksheets, DORA metric exercises, vendor-evaluation rubrics, CRM pipeline exercises, startup IT checklists, data-sovereignty review prompts, capstone marking rubrics, and current market notes.


Treat dated numbers with care. Salary ranges, certification details, vendor prices, legal thresholds, platform behaviour, and survey claims are useful examples only when they are current and sourced. When this book uses a live-market example, read it as a pattern to verify, not a promise that the number will still be true when you graduate.



\subsection{Case Ledger}


\begin{itemize}[leftmargin=*]
\index{support tiers}
\item \textbf{Coralline} is a fictional Brisbane online retailer used to introduce ITIL foundations, service value, support tiers, and major-incident work through Priya's entry-level service-desk perspective.
\index{change enablement}
\index{CMDB}
\index{continual improvement}
\index{ITIL!change enablement}
\index{ITIL!continual improvement}
\index{OLA}
\index{release management}
\item \textbf{Kestrel Freight} is a fictional Melbourne logistics company used for mature service management: SLAs, OLAs, change enablement, release management, CMDB practice, dashboards, and continual improvement.
\index{security baseline}
\item \textbf{Sarah's startup} is a fictional high-growth small company used for constrained IT judgement: domain setup, identity, device management, security baselines, vendor rhythm, due diligence, and enterprise-stack decisions.
\index{buying committee}
\item \textbf{Vendor and CRM scenarios} use fictional accounts and sales teams to show how buying committees, account executives, sales engineers, customer-success managers, and service teams hand work to one another.
\index{Te Hiku Media}
\item \textbf{Te Hiku Media and Indigenous data-governance examples} are not generic case fiction. They require careful sourcing, local context, and respect for the communities and frameworks being discussed.
\item \textbf{The capstone organisation} should be real enough that its constraints matter: funding cycle, staff capacity, data authority, risk tolerance, and support model.
\end{itemize}


\subsection{A Note On Indigenous Digital Sovereignty}


\index{CARE principles}
\index{kaitiakitanga}
\index{Maori}
\index{OCAP}
Part 7 introduces Indigenous-led frameworks and examples, including CARE, OCAP, tikanga-led governance, kaitiakitanga, and Te Hiku Media's language-technology work. It does not make one framework stand in for every Indigenous context. Māori, Aboriginal, Torres Strait Islander, First Nations, and other Indigenous communities have different histories, authorities, legal settings, and protocols. Publication use of this material should be reviewed with people who have relevant community authority or specialist expertise; classroom use should still treat the material as responsibility-bearing professional practice, not as an ethics box to tick.
\setcounter{secnumdepth}{2}

\tableofcontents
\mainmatter
\include{chapters/part-01-itil-4-foundations}
\include{chapters/part-02-itil-deep-dive}
\include{chapters/part-03-high-velocity-delivery}
\include{chapters/part-04-blameless-rca-continuous-improvement}
\include{chapters/part-05-vendor-msp-crm-lifecycle}
\include{chapters/part-06-start-ups-small-biz-it}
\include{chapters/part-07-open-source-indigenous-digital-sovereignty}
\include{chapters/part-08-project-studio-and-presentations}
\backmatter
\cleardoublepage
\phantomsection
\addcontentsline{toc}{chapter}{Index}
{\footnotesize\raggedright\printindex}
\end{document}
